\section{System Overview}
We consider a scenario where in a room every smartphone which normally has dual microphone as information receivers%PROBLEM:use plurality or singular?
is deployed in a localization system to estimate the location of the acoustic source. When the acoustic source make a sound, smartphone could give us one bit binary information by analyzing duplex sonic signal provided by the dual microphone on the smartphone. The one bit binary information the smartphone gives can tell us which of dual microphone on the smartphone the acoustic source is closer to. That is to say, when we use the perpendicular bisector of the dual microphone divide the area into two space, this one bit binary will tell us which space the acoustic source stay. Now we can regard the whole area as a big birthday cake. When we use one bit information, it is like we use the perpendicular bisector to cut the cake into two part and we only keep the part which has the acoustic source. Then we can use all of the smartphone in the room to 'cut the cake'. The last remaining area is the acoustic source area.\\%Basic area localization method
However, there are always some node can not give the authentic data which may influence the localization result. We need to find these bad node and remove them. Firstly, we need get an approximate acoustic source location. And then we can use the approximate location to do backwards to speculate weather the node are bad or not.\\
\subsection{Get the approximate acoustic source}
In the basic area localization method, we consider data of the all node are true. Nevertheless, the reality can not be what we want which means if we still trust all the data, we can get nothing. Our approach is to give little trust to every node. And this time when we do the localization again, even if there are some error node, we can still get approximate acoustic source location. 